---
title: "Mayo Clinic Yelp Review Text Analysis"
author: RexManglicmot
output: 
  github_document: 
    toc: yes

always_allow_html: true
---

## Status: Contnuing Working document
Hi everyone. I’m continuing building my data analysis and R skills. As such, I would love feedback to better improve this project via rexmanglicmot@gmail.com. Any mistakes and misrepresentation of the data are my own.

Things Need to Do/Questions:

* Need to create wordclouds
* Import and adjust dictionaries
* Fix overall grammar
* Need to List of the metrics in US News for evaluating hospitals and pick up where they left off or, pick up on what is missing in their analyses. 
* Need to find code to align left on the text column in the cleaning section
* Learn how to create a US heat map code in the EDA section
* learn how to remove file from Github (html document) but keep locally
* look for a dictionary that has Male and Female first names and run it agaisnt data to see how many of each gender is present in the reviews
* look for code how to highlight certain columns in a barchart (i.e., ratings barchart below)
* Create and cite sources of the benefits of wordclouds

## Introduction
<center>

![](https://target.scene7.com/is/image/Target/GUEST_1ec18fe8-25da-4ae9-a754-33f87564fdcb?wid=725&hei=725&qlt=80&fmt=webp) 

</center>

What is the best hospital within the US? Which one is the nearest to me? Where can find out what patients have to say about this XYZ hospital? These questions are sample of many questions as Americans navigate the maze of the US private healthcare hospital system. On average, health care spending is $12,530 per person in 2022, which is up from $11,462 in 2019.^[https://www.chcf.org/publication/2022-edition-health-care-costs-101/] With a total of 6,093 US hospitals^[https://www.aha.org/statistics/fast-facts-us-hospitals], it leaves many to wonder which healthcare system they should put their lives and money on. Unlike a single payer system, where the government covers majority of healthcare needs for its citizens (i.e. Canada, UK, and Australia), the US healthcare system is comprised of private and public conglomarate and individual hosptal systems. Therefore, in the US, not all hospitals are created equal as some are privately and publicized owned; some do well versus some do not. 

There is a need to rank such hospitals. Thus, every year U.S. News publishes the best hospitals ranked within the U.S.^[https://health.usnews.com/health-care/best-hospitals/articles/faq-how-and-why-we-rank-and-rate-hospitals] Although the list does not contain all the hospitals, but contained about 4500. The top ranked hospital for 2022-23 is the Mayo Clinic based on U.S. News methodology. To gain a better understanding why the Mayo Clinic is #1 and to further build upon this study, I decided to use anothe method to better understand and use a Text Analysis on comments made by Yelp reviewers as a means. 

Thus, this projects aims to understand user reviews through the Yelp platform, which is aimed to provide reviews to many businesses, including healthcare institutions (both private and public). By undergoing this research, there are 3 objectives:

1. Uncover hidden word-themes that reflect the true sentiments by patients that is also reproducible 
2. Provide a starting point for hospital C-suite to reflect some of the concerns patients have about their facility
3. Provide an opportunity for hospitals on the bottom part of the US News list to reflect on their services to patients 

By using text data, there are an array of methods to deploy. 

This project is comprised of the following chapters:

1. Webscraping Yelp Data
2. Loading the Libraries
3. Loading the Data
4. Cleaning the Data
5. Exploratory Data Analysis
6. Word Cloud
7. Positive and Negative Words
8. Limitations
9. Conclusion
10. Inspiration for this project

## Webscraping Yelp Data
Yelp data was scrapped on via the [Yelp](https://www.yelp.com/) website. Within the search engine bar, I typed in *Mayo Clinic* and used the first "business result to scrape the data as it's location, Rochester Minnesota matched on US News. Further, the business had a "blue-checkmark" with "Claimed" indicating that the business was the legitimate Mayo Clinic.

There were 228 reviews in total and the goal was to scrape all 228 reviews containing these 4 metrics:

1. reviewer name
2. reviewer location
3. review rating
4. review text

(I decided to exclude photos from the reviewers because of the scope of this project to analyze text data.) 

After various hours debugging the code and looking at html tags to discern appropriate tags to scrape, I was able to obtain all reviews within Yelp. Troubleshooting code included unintentionally scraping a response from a Mayo Clinic official that accrued in more than the 228 reviews. A special acknowledgement to Samer Jijjazi for his YouTube tutorial in learning how to scrape data from Yelp.^[https://www.youtube.com/watch?v=qyGYItbMKkM] Watching his videos greatly helped me get the data needed to webscrape.

Below is the code used to scrape data. Mayo_Clinic.csv file is available within the repository. 
```{r Webscraping Yelp data, eval=FALSE}

#load libraries
library(tidyverse)
library(rvest)

#create an object to store the webpage address
url <- 'https://www.yelp.com/biz/mayo-clinic-rochester-12?osq=Mayo+clinic'

#convert the url to an html object for R processing
webpage <- read_html(url)

#create object to know page number on the webpage
webpageNum <- webpage %>%
  html_elements(xpath = "//div[@class= ' border-color--default__09f24__NPAKY text-align--center__09f24__fYBGO']") %>%
  html_text() %>%
  str_extract('of.*') %>%
  str_remove('of ') %>%
  as.numeric()

#create a sequence to iterate for page number
webpageSeq <- seq(from = 0, to = (webpageNum * 10)-10, by = 10)

#store items into empty objects
reviewer_name_all = c()
reviewer_location_all = c()
review_rating_all = c()
review_text_all = c()

#create a for loop to get values throughout the 23 pages
for (i in webpageSeq) {
  #need to create an if statement because the 1st page web address
  if (i == 0) {
    webpage <- read_html(url)
    #need to create else because webpage has more content than 1st page web 
    #address
  } else {
    webpage <- read_html(paste0(url, '&start=', i))
  }
  
  #reviewer name
  reviewer_name <- webpage %>%
    #return elements that I specify via xpath method
    #xpath is useful for locating elements
    #// means to search within entire document
    #* means to return any of the elements
    # div means to search within document with the div tags
    html_elements(xpath = "//div[starts-with(@class,' user-passport')]") %>%
    #look within a tag within the previous element
    html_elements(xpath = ".//a[starts-with(@href, '/user_details')]") %>%
    html_text()
  
  #reviewer location
  reviewer_location <- webpage %>%
    #location is within the same div tag, so use same code
    html_elements(xpath = "//div[starts-with(@class,' user-passport')]") %>%
    #location is also located within the span tag
    html_elements(xpath = ".//span[@class= ' css-qgunke']") %>%
    html_text() %>%
    #remove "Location" 
    #pipe remaining values that are not "Location"
    .[. !='Location']
  
  #review rating
  review_rating <- webpage %>%
    html_elements(xpath = "//div[starts-with(@class, ' review')]") %>%
    #within div tag there is an aria-label
    #contains function to look for aria-label that has rating  
    html_elements(xpath = "(.//div[contains(@aria-label, 'star rating')])[1]")%>%
    #ratings are not text, so must use different method and specify which 
    #attribute to obtain
    html_attr('aria-label') %>%
    #remove star rating
    str_remove_all(' star rating') %>%
    #convert into a numeric
    as.numeric()
  
  #review text
  review_text <- webpage %>%
    html_elements(xpath = "//div[starts-with(@class, ' review')]") %>%
    #look throughout webpage with the p tag
    #to get the first comment and not worr about business comment,
    #need to put in brackets
    html_elements(xpath = "(.//p[starts-with(@class, 'comment')])[1]") %>%
    #html_elements(xpath = ".//span[starts-with(@class, ' raw')]") %>%
    html_text()
  
  #appending to appropriate objects
  reviewer_name_all = append(reviewer_name_all, reviewer_name)
  reviewer_location_all = append(reviewer_location_all, reviewer_location)
  review_rating_all = append(review_rating_all, review_rating)
  review_text_all = append(review_text_all, review_text)
  
}

#create a dataframe containing appended values
Mayo_Clinic <- data.frame('name' = reviewer_name_all,
                          'location' = reviewer_location_all,
                          'rating' = review_rating_all,
                          'text'= review_text_all)

#view csv file
#head(Mayo_Clinic)
```

## Loading the Libraries

```{r, message=FALSE, EDA }
#load libraries
#install.packages('tidyverse') #had to re-install for some reason on 11/12/22
#install.packages('ggraph') #had to re-install for some reason on 11/12/22
#install.packages('DT')
#install.packages('gt')

library(tidyverse)
library(tidytext)
library(widyr)
library(RColorBrewer)
library(wordcloud)
library(igraph)
library(ggraph)
library(gt)
```

## Loading the Data
```{r, message=FALSE}
#load Mayo Clinic data
data <- read.csv('Mayo_Clinic.csv')
```

## Cleaning the Data
Since the data is loaded, instead of using the function str, let's expand my R code competency by using different functions to view the column names and the dimensions of the the data
```{r}
#get the names of the variables
colnames(data)

#get the number of rows in the dataset
dim(data)
```
Ok, we see that there is the X variable which indexes the observations. Let's get rid of that column and check it if worked.

```{r}
#remove the X column
data <- data %>%
  select(-X)

#get the names other than the colnames funciton
names(data)
dim(data)
```

Good. Now, let's view the first few rows of the dataset using the head function.
```{r}
#View first rows of the observations of the data
head(data)

#how many observations are in the text column
length(data$text)
```
At first glance, we see that text column is empty except for the fifth observation. we also confirm the count of number of observations in the text column. However, we when slide the cursor to the right, we see that character strings are aligned right (this is a default function of the dataframe). Now, let's do a left-align to make the dataset easier to intepret. 
```{r }
#need to figure out how to align left on the text column
#wrong code below
#alignment(data, left = 'left')
```
Great, now let's see if there are duplicates AND if there is more than one reviewer in the dataset. 
```{r}
#check for duplicates
sum(duplicated(data))

#quick check to see if reviewer_name appears more than once
data %>%
  count(name, sort = TRUE) %>%
  #let's arbitarailys see the first 10 rows as base comparison
  head(n=10)
```
We see that there are no duplicates and 5 people gave a review twice, so a total of 223 different observations.

In cleaning our data, let's see if there are any NA values and which columns. 
```{r}
#if any NA, then where in the dataset
which(is.na(data))

#quick check to see and sum if any NA are in rating variable
sum(is.na(data))

```
As a last round for checking our data, the ratings are scaled from 1 to 5, let's check if there any numbers above and below
```{r}
#quick check to see if below 1 OR above 5
any(data$rating > 5 | data$rating <1)

#create functions
numbers_only <- function(x) !grepl("\\D", x)
letters_only <- function(x) !grepl("[^A-Za-z]", x)

#let's double check the ratings column
sum(numbers_only(data$rating))
sum(letters_only(data$rating))

```
Now, that the data is cleaned thoroughly, let's explore the data. 

## Exploratory Data Analysis

One of the first questions that came to mine was where these reviewers lived. Are they local residents near the Mayo Clinic or are they visting? I think answering this question could provide more detal about the reviews. So, let's take the location column and graph it in the context of the US. But first, let's create a new object for this data exploration
```{r}
data_map <- data
```




The next question is to undertand patient ratings. So, let's take the a summary of that. 
```{r}
#calculate summary statistics
summary(data$rating)
```
Looking at the summary statistics we see that the median and the max of the list is 5. What this means is that there are more of the 5 "ratings" in the list than there are others. The best way to view this, is via the barchart. 
```{r}
#create a barchart to count the values
ggplot(data, aes(x=rating)) +
  geom_bar(color='black', fill='steelblue') +
  scale_fill_brewer(palette="Dark2") +
  theme_minimal() +
  labs(title = 'Yelp Review Ratings',
        x = 'Star Ratings',
        y = 'Count')
```

Great. We see visually that there are more 1 and 5 ratings than there are 2, 3, or 4. What this means is that patients had extreme views of the hospital (with respect to the ratings category); "good" and "not good", so to speak. 

Let's get the actual values of these counts by building a table.
```{r}
#create dataframe to build stacked barchart
rating <- c(1,2,3,4,5)
total <- c((sum(data$rating == 1)),
           (sum(data$rating == 2)),
          (sum(data$rating == 3)),
          (sum(data$rating == 4)),
          (sum(data$rating == 5)))

#create a table of all the rating sums
table3 <-data.frame(rating, total)
print(table3)
```
Now we see that for the 1 rating there are 72 reviews and for the 5 rating there are 121 (about 80%). Numerically, it seems the hospital has done relatively well. 

What we can do for the next steps are to separate the 228 reviews into 3 sections; 1 rating, 5 rating, and overall rating and see what words are associated within each. That would be interesting to figure out. 

## WordCloud

WordClouds are used to illustrate common words about a subject (Mayo Clinic in our case). Need to fill in more. 


In order to make a wordcloud, we need to index each word within a given sentence per reviwer into a separate observation for counting purposes. As a result, the number of observations in our current dataset, 228, will increase by alot.
```{r}


```




Because meanings of an English sentence is an accumulation of words. There are certain words that have no substantial meaning (filler words) like for example, words like "the, a, an, of, etc.", so we need to do a bit of more data cleaning to make an effective wordcoud. 
```{r}


```


## Limitations

## Conclusions

## Inspiration for this project


